preprocessing

### 2022-10-24 r-prep/prep.Rmd
working files
data base

---
title: "data import"
output: pdf_document
date: "2022-10-24"
---

@@

"hi" %>% print()

>>>>

---
title: "preprocessing"
output: pdf_document
date: "2022-10-24"
---

@@

```{r}
data_gwp100 = read_excel("data-raw/essd_ghg_data_gwp100.xlsx",sheet = "data")
load("data-raw/data_wdi.RData") 
data_wdi %<>% select(-country)

data_base = data_gwp100 %>% left_join(data_wdi,by=c("ISO","year"))

save(data_base,file="data-transf/data_base.RData")
```
